### 2017-07-17 01-intro.tex
Comments Henri on what's new&unpublished

A bird's-eye view of the work in this paper, without any technical detail, has been
published at CCGrid-2016~\cite{10.1109/CCGrid.2016.98}. The technical description and
evaluation of our accelerator contributions, which make up half of this paper's
content, have not been published before.
The results of our distributed contribution
have been previously published at the 2016 ParLearning
workshop~\cite{DBLP:conf/ipps/El-HelwHLAWB16}, where it earned a best-paper
award.

>>>>

A bird's-eye view of the work in this paper, without any technical detail, has been
published at CCGrid-2016~\cite{10.1109/CCGrid.2016.98}. The technical descriptions
in Section~\ref{sec-gpu-design} and evaluation of our accelerator contributions in
Section~\ref{sec-gpu-evaluation} and Figures \ref{gpu-sweep}, \ref{gpus-fig}
and~\ref{gpus-v-sweep} have not been published before.
The results of our distributed contribution
have been previously published at the 2016 ParLearning
workshop~\cite{DBLP:conf/ipps/El-HelwHLAWB16}, where it earned a best-paper
award. In summary, nearly half of the work in this paper consists of new, unpublished
material.

### 2017-07-17 gpu-05-03-accelerator.tex
Comments Henri on what's new&unpublished

\subsubsection{Analysis of GPU Parallelism}
As discussed in Section~\ref{gpu-design}, there are 10 distinct flavors of the
GPU version of the algorithm: the naive strategy, the
shared strategy, and 8 variations of the code generation strategy. This
section investigates the effectiveness of each flavor on NVidia's GTX~\mbox{Titan-X}
(Maxwell and Pascal),
GTX980, K40c and~K20m.

>>>>

\subsubsection{Analysis of GPU Parallelism}
\label{sec-gpu-analysis}

As discussed in Section~\ref{gpu-design}, there are 10 distinct flavors of the
GPU version of the algorithm: the naive strategy, the
shared strategy, and 8 variations of the code generation strategy. This
section investigates the effectiveness of each flavor on NVidia's GTX~\mbox{Titan-X}
(Maxwell and Pascal),
GTX980, K40c and~K20m.
